---
title: "Political Positions of MPs in the Tunisian Parliament"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    social: [ "twitter", "facebook", "menu" ]
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(reshape2)
library(ggplot2)
library(magrittr)
library(emIRT)
library(arpshiny)

data("all_matrices")
data("info_legis")
data("model_results")

# Fix a data typo
info_legis$legis.names[112] <- 'Mbarka Aouania'

model1_data <- data.frame(MP=info_legis$legis.names,Party=info_legis$Party,Highest_Ideal_Point=model_results[[1]]$means$x[,1] + 1.96*model_results[[1]]$bse$x,Average_Ideal_Point=model_results[[1]]$means$x[,1],
                          Lowest_Ideal_Point=model_results[[1]]$means$x[,1] - 1.96*model_results[[1]]$bse$x)
model2_data <- data.frame(MP=info_legis$legis.names,Highest_Ideal_Point=model_results[[2]]$means$x[,1] + 1.96*model_results[[2]]$bse$x,Party=info_legis$Party,Average_Ideal_Point=model_results[[2]]$means$x[,1],
                          Lowest_Ideal_Point=model_results[[2]]$means$x[,1] - 1.96*model_results[[2]]$bse$x)
model_data <- list(model1_data,model2_data)

graph_labels <- list(model1=c('Pro-\nGovernment','Moderate','Pro-\nOpposition'),
                     model2=c('Pro-\nGovernment','Moderate','Pro-\nOpposition'))
  
graph_breaks <-  list(model1=c(-2 * sd(model1_data$Average_Ideal_Point),0,
                       2*sd(model1_data$Average_Ideal_Point)),
                      model2=c(-2 * sd(model2_data$Average_Ideal_Point),0,
                       2 * sd(model2_data$Average_Ideal_Point)))



make_round <- function(x) {
  save_names <- colnames(x)
  small_func <- function(y) {
    if(is.numeric(y))
      y <- round(y,digits=3)
    y
  }
  x <- as.data.frame(lapply(x,small_func))
  names(x) <- save_names
  x
}
model_data <- lapply(model_data,make_round)
party_types <- levels(info_legis$Party)
legis_names <- info_legis$legis.names
num_rows <- nrow(model_data[[1]])


data_plots <- reactive({
      choice <- switch(input$var,"Yes vs. No"=1,"Yes/No vs. Abstain"=2)
      return(choice)
    })
  subset_filter <- reactive({
    if(!is.null(input$MP_names)) {
      return(input$MP_names)
  } else if("All" %in% input$parties) {
      return(NULL)
  } else {
      return(input$parties)
    }
  })
  subset_type_filter <- reactive({
    if(is.null(input$MP_names)) {
      return('party')
    } else {
      return('individual')
    }
  })
  
  

```

Estimated Models
======================================================================

Column {.sidebar}
------------------------------------------
Interact with a model of the Assemblee Representative du Peuple of Tunisia. This model puts Tunisian MPs on a political spectrum based on their voting record in the current parliament from Bawsala's [Marsad Majles](http://majles.marsad.tn/2014/?) data repository. It was created by [Robert Kubinec](http://sites.google.com/a/virginia.edu/robert-m-kubinec/) from the University of Virginia using the emIRT package in R by [Kosuke Imai, James Lo & Jonathan Olmsted, 2016](http://imai.princeton.edu/research/files/fastideal.pdf).

Use the provided options to select a model that either predicts yes vs. no votes or a model that predicts whether MPs will abstain from voting. Also use the options below the chart to change the appearance of the plot. Individual data for MPs is available from the [Raw Data for MPs] tab.


```{r}
      selectInput("var", label = "Choose a type of vote to predict",
                  choices = c("Yes vs. No","Yes/No vs. Abstain"),
                  selected = "Yes vs. No")

      p("A PDF version of the chart can be downloaded by clicking the button below.")
      
      downloadHandler(filename = 'Ideology Chart of the ARP.pdf',
                content = function(file) {
                  ggsave(file,plot(x=model_results[[data_plots()]],legis.names=model_data[[data_plots()]]$MP,
                        parties=model_data[[data_plots()]]$Party,subset_name=subset_filter(),
                        hjust_top=input$top_hjust,hjust_bottom=input$bottom_hjust,subset_type=subset_type_filter(),
                         x_axis_labels=graph_labels[[data_plots()]]),
                        width=10,height=16,units="in")})
      
      

```


Column
-----------------------------------------

### Ideology Plot {.no-title data-height=650}

```{r}
      renderPlot({ plot(x=model_results[[data_plots()]],legis.names=model_data[[data_plots()]]$MP,
                                           parties=model_data[[data_plots()]]$Party,subset_name=subset_filter(),
                      hjust_top=input$top_hjust,hjust_bottom=input$bottom_hjust,subset_type=subset_type_filter(),
                      x_axis_labels=graph_labels[[data_plots()]])},
                 bg='transparent')
```


### Display Options
```{r}
  
      checkboxGroupInput("parties",label="Choose a bloc to display",
                  choices=c("All",party_types),
                  selected="All",inline=TRUE)
      
      selectizeInput('MP_names',label="Select one or more MPs to display",choices=legis_names,multiple=TRUE)
      sliderInput('top_hjust',"Adjust MP names' position (top);",
                  min=-5,max=5,step=0.1,value=1.5)
      
      
      sliderInput('bottom_hjust',"Adjust MP names' position (bottom)",
                  min=-5,max=5,step=0.1,value=-0.5)

```


Raw Data for MPs
=========================================

To return to the model, go to the [Estimated Models] tab.

```{r}
DT::renderDataTable({model_data[[switch(input$var,"Yes vs. No"=1,"Yes/No vs. Abstain"=2)]]},rownames=FALSE) 
# renderTable({model_data[[switch(input$var,"Yes vs. No"=1,"Yes/No vs. Abstain"=2)]]})
```


About the Methodology
========================================

Column
-----------------------------------------------

### About the Model {.no-title}

This statistical model plots the underlying positions of MPs in the Tunisian National Assembly by comparing their votes across nearly 1700 amendments and bills in the current parliament. The model only incorporates votes and for that reason is not necessarily a statement about each individual MP's ideology. Rather, it reflects the alliances within the parliament and how those alliances between blocs and parties have led to divergent voting records. Broadly speaking, the parliament breaks down into the government (Nidaa Tounes, Nahda, Afek Tounes, UPL) and the opposition (Social Democrats, Front Populaire, Independents). However, there is considerable diversity within parties and also within these larger groups. Some of that diversity can be explored by looking at the model that predicts when MPs will abstain on legislation: this model is more likely to show the differences that exist within parties.


